Exclusions

### 2018-08-30 E2/analysis/exclusions.Rmd
Better fixed

#Add R parameter estimates to data tibble
#To merge them, unfortunately have to convert to dataframe first because dplyr has no binding of tibbles.
# https://stackoverflow.com/questions/45643886/how-to-combine-tibbles-with-common-but-non-identical-columns#45644319
#Not sure what is lost as a result.
dd<- as_data_frame(data)
es<- as_data_frame(estimates)
#Looks like each subject has only 8 efficacy values somehow, it's because there was an extra
#variable, X
es$X <- NULL
dat<- merge(dd,es)
dg<-dat %>% filter( !is.na(targetSP) ) #excluding 1-target trials rows reporting stream on opposite side. Eventually, use those to evaluate swaps.
```

@@

twoTarget<- dg %>% filter(targetSide=="Both")

@@

Will also exclude if difference in efficacy left-right exceeds?
```{r }
#Calculate exclusions based on one-target performance
oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Look at the difference in efficacy between the left and the right
effDiff <- function(df) {
  #dgi<<-df
  #STOP
  effLeft<- (df %>% filter(targetSide=="Left"))$efficacy 
  effRight<- (df %>% filter(targetSide=="Right"))$efficacy
  df$effDiff<- effLeft - effRight
  df$effLeft <- effLeft; df$effRight <- effRight

@@

  failedBothLR <- ((df %>% filter(targetSide=="Left"))$pLRtest >= .05) &
    ((df %>% filter(targetSide=="Right"))$pLRtest >= .05)
  df$failedBothLR <- failedBothLR

@@

```{r}
#To do that, do I'd either need to unmelt (spread) but rather than do that, I programmed putting effLeft and effRight on same row into effDiff
g<- ggplot(oneDiff, aes(x=effLeft, y=effRight, color=orientation)) + geom_point()
g<-g +  geom_abline(intercept = 0, slope = 1) + theme_apa() + xlim(0,1) + ylim(0,1)
g +    geom_rug(col=rgb(.5,0,0,alpha=.2))

@@

```{r exclude, echo=FALSE}
allLosers <- unique( c(LRtestLosers, lowEffLosers, oneTargetLosers) )
#afterExclusions<- dat %>% filter(  !(subject %in% lowEffs)   )
dat <- dat %>% mutate(exclude = (subject %in% allLosers))
#table(dat$subject,dat$exclude)
```

@@

```{r exclude, echo=FALSE}

pathToSave <- file.path( "..","Data")
saveRDS(dat, file.path(pathToSave,"backwards2E2_dataWithEstimatesAndExcludeColumn.rda"), compress = "bzip2")
```

>>>>

#Add R parameter estimates to data tibble
#To merge them, unfortunately have to convert to dataframe first because dplyr has no binding of tibbles.
# https://stackoverflow.com/questions/45643886/how-to-combine-tibbles-with-common-but-non-identical-columns#45644319
#Not sure what is lost as a result.
dd<- as_data_frame(data)
es<- as_data_frame(estimates)
#Looks like each subject has only 8 efficacy values somehow, it's because there was an extra
#variable, X
es$X <- NULL
#oldNoNa<- merge(dd,es) #loses the is.na(targetSP) rows
dat<- merge(dd,es, all = TRUE)
dg<-dat %>% filter( !is.na(targetSP) ) #excluding 1-target trials rows reporting stream on opposite side. Eventually, use those to evaluate swaps.

Merge operation lost it  targetSP==NA in data? That's the rows reporting stream on opposite side. Eventually, use those to evaluate swaps. I don't know what happened to it, because it's created in 
exclusions.Rmd, which on line 67 creates the thing merged with estimates that is saved. 
```{r, echo=FALSE}
table(dat$targetSP,useNA="ifany")

#dat %>% filter( is.na(targetSP) )
```

@@

twoTarget<- dg %>% filter(targetSide=="both")

@@

Will also exclude if difference in efficacy left-right exceeds?
```{r }
#Calculate exclusions based on one-target performance
oneTarget<- dg %>% filter(targetSide!="both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Look at the difference in efficacy between the left and the right
effDiff <- function(df) {
  #dgi<<-df
  #STOP
  effLeft<- (df %>% filter(targetSide=="left"))$efficacy 
  effRight<- (df %>% filter(targetSide=="right"))$efficacy
  df$effDiff<- effLeft - effRight
  df$effLeft <- effLeft; df$effRight <- effRight

@@

  failedBothLR <- ((df %>% filter(targetSide=="left"))$pLRtest >= .05) &
    ((df %>% filter(targetSide=="right"))$pLRtest >= .05)
  df$failedBothLR <- failedBothLR

@@

```{r}
#To do that, do I'd either need to unmelt (spread) but rather than do that, I programmed putting effLeft and effRight on same row into effDiff
library(ggplot2)
g<- ggplot(oneDiff, aes(x=effLeft, y=effRight, color=orientation)) + geom_point()
g<-g +  geom_abline(intercept = 0, slope = 1) + theme_bw() + xlim(0,1) + ylim(0,1)
g +    geom_rug(col=rgb(.5,0,0,alpha=.2))

@@

```{r excludeAll, echo=FALSE}
allLosers <- unique( c(LRtestLosers, lowEffLosers, oneTargetLosers) )
#afterExclusions<- dat %>% filter(  !(subject %in% lowEffs)   )
dat <- dat %>% mutate(exclude = (subject %in% allLosers))
#table(dat$subject,dat$exclude)
```

@@

```{r exclude, echo=FALSE}
pathToSave <- file.path( "..","Data")
saveRDS(dat, file.path(pathToSave,"backwards2E2_dataWithEstimatesAndExcludeColumn.rda"), compress = "bzip2")
```
